### 2022-07-30 latex/Chapters/Examples.tex

\afblue
\paragraph{}{\textbf{python code -- deep learner}}
\begin{python}
####################################################################
from math import inf
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deeplearner import DeepLearner
from rubiks.puzzle.puzzle import Puzzle
from rubiks.puzzle.trainingdata import TrainingData
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n = 5
    m = 2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus = 4
    time_out = 600
    nb_shuffles = inf
    nb_sequences = 100
    TrainingData(**globals()).generate(**globals())
    """ DL learner """
    action_type = Learner.do_learn
    learner_type = Learner.deep_learner
    nb_epochs = 999
    learning_rate = 1e-3
    optimiser = DeepLearner.rms_prop
    scheduler = DeepLearner.exponential_scheduler
    gamma_scheduler = 0.9999
    save_at_each_epoch = False
    threshold = 0.01
    training_data_freq = 100
    high_target = nb_shuffles + 1
    training_data_from_data_base = True
    nb_shuffles_min = 20
    nb_shuffles_max = 50
    nb_sequences = 50
    """ ... and its network config """
    network_type = DeepLearning.fully_connected_net
    layers_description = (100, 50, 10)
    one_hot_encoding = True
    """ Kick-off the Deep Learner """
    learning_file_name = Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ Plot its learning """
    action_type = Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black

@@

\afblue
\paragraph{}{\textbf{python code -- deep reinforcement learner}}
\begin{python}
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deepreinforcementlearner import DeepReinforcementLearner
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n = 4
    m = 2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus = 4
    """ DRL learner """
    action_type = Learner.do_learn
    learner_type = Learner.deep_reinforcement_learner
    nb_epochs = 25000
    nb_shuffles = 50
    nb_sequences = 10
    training_data_every_epoch = False
    cap_target_at_network_count = True
    update_target_network_frequency = 500
    update_target_network_threshold = 1e-3
    max_nb_target_network_update = 40
    max_target_not_increasing_epochs_pct = 0.5
    max_target_uptick = 0.01
    learning_rate = 1e-3
    scheduler = DeepReinforcementLearner.exponential_scheduler
    gamma_scheduler = 0.9999
    """ ... and its network config """
    network_type = DeepLearning.fully_connected_net
    layers_description = (128, 64, 32)
    one_hot_encoding = True
    """ Kick-off the Deep Reinforcement Learner ... """
    learning_file_name = Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ ... and plot its learning data """
    action_type = Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black
As can be seen on the next page, which I obtained from running the above code snipet (keep in mind that every run is going to be slightly different due to the random puzzles being generated), the training stopped after about 17,100 epochs as the 40 target network updates had been reached. By that point, the DRL learner had seen 40\% of the possible puzzles, and the very last MSE loss (after update, so out-of-sample) was around 0.4, corresponding to 2\% of the max target cost. It is interesting to notice that since I have shuffled the sequences only 50 times, and since the (n=4, m=2) SP is quite constrained in terms of possible moves, the max target ever produced by the network was only around 25, whereas we know the God number for this dimension is 36 (see later section \ref{sec:SPLowDimension}). It is therefore likely that the resulting network would not produce very optimal solutions for puzzles whose cost is in the region [25, 36].

@@

%-----------------------------------
%	SUBSECTION 2.1
%-----------------------------------
\subsection{Blind search}
%-----------------------------------
%	SUBSECTION 2.1.1
%-----------------------------------
\subsubsection{BFS}
\label{BFSSS}
%-----------------------------------
%	SUBSECTION 2.1.2
%-----------------------------------
\subsubsection{DFS}
\label{DFSSS}

@@

As a comparison point for other sliding puzzle solvers, I have implemented a naive sliding puzzle solver, which does what most beginner players would intuitively do when solving the sliding puzzle by hand: solve the top row, then the left column, and keep iterating until done. Notice that once either the top row or left column is solved, there is no longer any need to modify it, we have simply reduced the problem to a sub-problem of reduced dimension. For the interested reader, the details of the algorithm are as follows:

>>>>

\afblue
\paragraph{}{\textbf{python code -- deep learner}}
\begin{python}
####################################################################
from math import inf
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deeplearner import DeepLearner
from rubiks.puzzle.puzzle import Puzzle
from rubiks.puzzle.trainingdata import TrainingData
####################################################################
if '__main__' == __name__:
    puzzle_type=Puzzle.sliding_puzzle
    n=5
    m=2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus=4
    time_out=600
    nb_shuffles=inf
    nb_sequences=100
    TrainingData(**globals()).generate(**globals())
    """ DL learner """
    action_type=Learner.do_learn
    learner_type=Learner.deep_learner
    nb_epochs=999
    learning_rate=1e-3
    optimiser=DeepLearner.rms_prop
    scheduler=DeepLearner.exponential_scheduler
    gamma_scheduler=0.9999
    save_at_each_epoch=False
    threshold=0.01
    training_data_freq=100
    high_target=nb_shuffles + 1
    training_data_from_data_base=True
    nb_shuffles_min=20
    nb_shuffles_max=50
    nb_sequences=50
    """ ... and its network config """
    network_type=DeepLearning.fully_connected_net
    layers_description=(100, 50, 10)
    one_hot_encoding=True
    """ Kick-off the Deep Learner """
    learning_file_name=Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ Plot its learning """
    action_type=Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black

@@

\afblue
\paragraph{}{\textbf{python code -- deep reinforcement learner}}
\begin{python}
####################################################################
from rubiks.deeplearning.deeplearning import DeepLearning
from rubiks.learners.learner import Learner
from rubiks.learners.deepreinforcementlearner import DeepReinforcementLearner
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type=Puzzle.sliding_puzzle
    n=4
    m=2
    """ Generate training data - 100 sequences of fully 
    solved perfectly shuffled puzzles. 
    """
    nb_cpus=4
    """ DRL learner """
    action_type=Learner.do_learn
    learner_type=Learner.deep_reinforcement_learner
    nb_epochs=25000
    nb_shuffles=50
    nb_sequences=10
    training_data_every_epoch=False
    cap_target_at_network_count=True
    update_target_network_frequency=500
    update_target_network_threshold=1e-3
    max_nb_target_network_update=40
    max_target_not_increasing_epochs_pct=0.5
    max_target_uptick=0.01
    learning_rate=1e-3
    scheduler=DeepReinforcementLearner.exponential_scheduler
    gamma_scheduler=0.9999
    """ ... and its network config """
    network_type=DeepLearning.fully_connected_net
    layers_description=(128, 64, 32)
    one_hot_encoding=True
    """ Kick-off the Deep Reinforcement Learner ... """
    learning_file_name=Learner.factory(**globals()).get_model_name()
    Learner.factory(**globals()).action()
    """ ... and plot its learning data """
    action_type=Learner.do_plot
    Learner.factory(**globals()).action()
####################################################################
\end{python}
\black
As can be seen on the next page, which I obtained from running the above code snipet (keep in mind that every run is going to be slightly different due to the random puzzles being generated), the training stopped after about 17,100 epochs as the 40 target network updates had been reached. By that point, the DRL learner had seen 40\% of the possible puzzles, and the very last MSE loss (after update, so out-of-sample) was around 0.4, corresponding to 2\% of the max target cost. It is interesting to notice that since I have shuffled the sequences only 50 times, and since the (n=4, m=2) SP is quite constrained in terms of possible moves, the max target ever produced by the network was only around 25, whereas we know the God number for this dimension is 36 (see later section \ref{sec:SPLowDimension}). It is therefore likely that the resulting network would not produce very optimal solutions for puzzles whose cost is in the region [25, 36].

@@

%-----------------------------------
%	SUBSECTION 2.1
%-----------------------------------
\subsection{Blind search}
First let me start with some of the blind search algorithms, which I only have been able to use on small dimension SP. They quickly become too memory hungry to be practical on anything but the smallest puzzles.
%-----------------------------------
%	SUBSECTION 2.1.1
%-----------------------------------
\subsubsection{BFS}
\label{BFSSS}
The following example shows how to use Breadth First Search to solve a (n=3, m=3) SP which we do not \textit{shuffle} too much.

\afblue
\paragraph{}{\textbf{python code -- breadth first search solver}}
\begin{python}
####################################################################
from rubiks.solvers.solver import Solver
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n=3
    m=3
    nb_shuffles=10
    solver_type=Solver.bfs
    check_optimal=True
    action_type=Solver.do_solve
    print(Solver.factory(**globals()).action())
####################################################################
\end{python}
\black

As expected (since BFS is optimal), the solution found, printed by the snipet of code above, is optimal. The check\_optimal flag in the code snipet indicates that the solver should let us know if solution is optimal. Since BFS advertises itself (via the Solver base class API)  as an optimal solver, the solution is deemed optimal.

\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{./Figures/examplebfssolver}
%\decoRule
\caption[Examples]{breadth first search solver example}
\label{fig:examplebfssolver}
\end{figure}

%-----------------------------------
%	SUBSECTION 2.1.2
%-----------------------------------
\subsubsection{DFS}
\label{DFSSS}

\afblue
\paragraph{}{\textbf{python code -- depth first search solver}}
\begin{python}
####################################################################
from rubiks.solvers.solver import Solver
from rubiks.puzzle.puzzle import Puzzle
####################################################################
if '__main__' == __name__:
    puzzle_type = Puzzle.sliding_puzzle
    n=3
    m=3
    nb_shuffles=8
    limit=15
    time_out=60
    solver_type=Solver.dfs
    check_optimal=True
    log_solution=True
    action_type=Solver.do_solve
    Solver.factory(**globals()).action()
####################################################################

\end{python}
\black
Here we can see, in contrast with the previous example, that the solution obtained by DFS is not optimal. The Solver indicates it and shows an optimal solution. Clearly since we shuffled 8 times from goal configuration, the optimal path cannot have a cost higher than 8 (it could be lower though of course).

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{./Figures/exampledfssolver}
%\decoRule
\caption[Examples]{depth first search solver example}
\label{fig:exampledfssolver}
\end{figure}

@@

As a comparison point for otherSP solvers, I have implemented a naive sliding puzzle solver, which does what most beginner players would intuitively do when solving the sliding puzzle by hand: solve the top row, then the left column, and keep iterating until done. Notice that once either the top row or left column is solved, there is no longer any need to modify it, we have simply reduced the problem to a sub-problem of reduced dimension. For the interested reader, the details of the algorithm are as follows:

### 2022-07-30 latex/Chapters/SlidingPuzzle.tex
update

As mentioned in chapter \ref{sec:Puzzles}, the state space cardinality for the SP grows very quickly with n and m. Here are the only dimensions which have less than 239.5 millions states. Note I am also only considering n $\leq$ m since (p, q) can always be solved if we know how to solve (q, p):
\\
\\
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 12 & 360 & 20,160 & 1,814,400 \\
3              &   &   & 181,440 &  &    \\
\end{tabular}
\end{center}
In this section, I will discuss \textbf{full} results for these 5 puzzles. In order to fully solve them, one can simply use rubiks.scripts.learner, setting up the PerfectLearner with A* and manhattan heuristic, or instantiate directly a PerfectLearner as have seen in section \ref{PLSS}
I obtained the following God numbers for these puzzles:
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 6 & 21 & 36 &  \\
3              &   &   & 31 &  &    \\
\end{tabular}
\end{center}
and the most difficult puzzles (requiring a number of steps equal to their respective God number to solves):
\\
\\
\underline{Most difficult 2x2 (6 moves)}:
\begin{center}
\begin{three}
\setrow{2}{,3}
\setrow{1}{2,1}
\end{three}
\end{center}
\underline{Most difficult 2x3 (21 moves)}:
\begin{center}
\begin{five}
\setrow{2}{4,5,}
\setrow{1}{1,2,3}
\end{five}
\end{center}
\underline{Most difficult 2x4 (36 moves)}:
\begin{center}
\begin{seven}
\setrow{2}{,7,2,1}
\setrow{1}{4,3,6,5}
\end{seven}
\end{center}
\underline{Most difficult 2x5 (47 moves) .... TBD }:
\begin{center}
\begin{nine}
\setrow{2}{,2,7,4,1}
\setrow{1}{5,8,3,9,6}
\end{nine}
\end{center}
\underline{Most difficult 3x3 (31 moves)}:
\begin{center}
\begin{eight}
\setrow{3}{8,6,7}
\setrow{2}{2,5,4}
\setrow{1}{3,,1}
\end{eight}
\end{center}

@@

\subsection{Solvers' comparison}
\label{ssec:33SPSC}
Finally, to conclude this section on the 3x3 case, let me discuss a comparison of several algorithms on 1000 random puzzles generated for a number of random shuffling (with best effort no backtracking) from 0 to 50 in step of 2, as well as for perfect shuffling (denoted by $\infty$) on the comparison graphs. The results are shown in figure \ref{fig:33SPPerformance}

>>>>

As mentioned in chapter \ref{sec:Puzzles}, the state space cardinality for the SP grows very quickly with n and m. Here are the only dimensions which have less than 239.5 millions states. Note I am also only considering n $\leq$ m since (p, q) can always be solved if we know how to solve (q, p):
\\
\\
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 12 & 360 & 20,160 & 1,814,400 \\
3              &   &   & 181,440 &  &    \\
\end{tabular}
\end{center}
In this section, I will discuss \textbf{full} results for these 5 puzzles. In order to fully solve them, one can simply use rubiks.scripts.learner, setting up the PerfectLearner with A* and manhattan heuristic, or instantiate directly a PerfectLearner as have seen in section \ref{PLSS}
I obtained the following God numbers for these puzzles:
\begin{center}
\begin{tabular}{l*{6}{c}r}
n              & m & 2 & 3 & 4 & 5\\
\hline
2              &   & 6 & 21 & 36 & 51* \\
3              &   &   & 31 &  &    \\
\end{tabular}
\end{center}
* provisional result
\\
\\
and the most difficult puzzles (requiring a number of steps equal to their respective God number to solves):
\\
\\
\underline{Most difficult 2x2 (6 moves)}:
\begin{center}
\begin{three}
\setrow{2}{,3}
\setrow{1}{2,1}
\end{three}
\end{center}
\underline{Most difficult 2x3 (21 moves)}:
\begin{center}
\begin{five}
\setrow{2}{4,5,}
\setrow{1}{1,2,3}
\end{five}
\end{center}
\underline{Most difficult 2x4 (36 moves)}:
\begin{center}
\begin{seven}
\setrow{2}{,7,2,1}
\setrow{1}{4,3,6,5}
\end{seven}
\end{center}
\underline{Most difficult 2x5 (51* moves)}:
\begin{center}
\begin{nine}
\setrow{2}{,3,4,2,6}
\setrow{1}{5,9,8,7,1}
\end{nine}
\end{center}
* provisional result
\\
\\
\underline{Most difficult 3x3 (31 moves)}:
\begin{center}
\begin{eight}
\setrow{3}{8,6,7}
\setrow{2}{2,5,4}
\setrow{1}{3,,1}
\end{eight}
\end{center}

@@

\subsection{Solvers' comparison}
\label{ssec:33SPSC}
Let me discuss a comparison of several algorithms on 1000 random puzzles generated for a number of random shuffling (with best-effort-no-backtracking) from 0 to 50 in step of 2, as well as for perfect shuffling (denoted by $\infty$) on the comparison graphs. The results are shown in figure \ref{fig:33SPPerformance}

### 2022-07-30 latex/MScAIFrancoisBerrier.tex
update

\newcommand{\red}{\color{red}}
\newcommand{\black}{\color{black}}
\newcommand{\blue}{\color{blue}}
\newcommand{\green}{\color{green}}

@@

@@

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------

%\begin{declaration}
%\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
%\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

%\begin{itemize} 
%\item This work was done wholly or mainly while in candidature for a research degree at this University.
%\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
%\item Where I have consulted the published work of others, this is always clearly attributed.
%\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
%\item I have acknowledged all main sources of help.
%\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
%\end{itemize}

%\noindent Signed:\\
%\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

%\noindent Date:\\
%\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
%\end{declaration}

%\cleardoublepage

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
\textbf{Motivation}
\\
Reinforcement Learning (\textbf{RL}), exposed with brilliant clarity in the Sutton book (\cite{Sutton1998}), has until recently known less success than we might have hoped for. Its framework is very appealing and intuitive. In particular, the mathematical beauty of Value iteration and Q iteration (\cite{WatkinsThesis}) for discrete state and action spaces, blindly iterating from \textit{any} initial value, is quite profound. Sadly, it had until recently proven hard to achieve practical success with these methods.
\\
Inspired however by the seminal success of Deep Mind's team in using Deep Reinforcement Learning (\textbf{DRL}) to play Atari games (\cite{Mnih2013})  and to master the game of Go (\cite{AlphaGo}), researchers have in recent years made a lot of progress towards designing algorithms capable of learning and solving, \textit{without human knowledge}, the Rubiks Cube (\textbf{RC}) - as well as similar single player puzzles - by using Deep Q-Learning (\textbf{DQR})  (\cite{DBLP:journals/corr/abs-1805-07470}) or search and (\textbf{DRL}) value iteration (\cite{https://doi.org/10.48550/arxiv.1805.07470}).
\\
In this project, I will attempt to implement a variety of solvers combining $A^{*}$ search and heuristics, some of which will be handcrafted, others which I will train on randomly generated sequences of puzzles using (\textbf{DL}) or (\textbf{DRL}), to solve the 15-puzzle (and variations of different dimensions), as well as the Rubik's cube.
\\
\\
\textbf{Organisation of this thesis}
\\
In the first chapter, I will quickly describe what I hope to get out of this project, both in terms of personal learning, as well as in terms of tangible results (solving some puzzles!). In chapter 2, I will do a quick recap of the different methods that I will use in the project. Chapter 3 will be dedicated to discussing the mathematics of the sliding puzzle (\textbf{SP}) and the (\textbf{RC}). I might throw a few random (but hopefully interesting) observations in there and give some references for the keen reader. I will then give an overview in chapter 4 of the code base I have developed - and put in the open on my github page (\cite{FB}) - to complete this project before detailing a few examples in chapter 5. Finally, in chapters 6 and 7, I will present all my various results on respectively the sliding puzzle and the Rubiks' cube.

@@

\textbf{AIPnT} & \textbf{A}rtificial \textbf{I}ntelligence \textbf{P}rinciples and \textbf{T}echniques\\
\textbf{CS} & \textbf{C}omputer \textbf{S}cience\\
\textbf{CV} & \textbf{C}omputer \textbf{V}ision\\
\textbf{DL} & \textbf{D}eep \textbf{L}earning\\
\textbf{DQL} & \textbf{D}eep \textbf{Q}-\textbf{L}earning\\
\textbf{DRL} & \textbf{D}eep \textbf{R}einforcment \textbf{L}earning\\
\textbf{ML} & \textbf{M}achine \textbf{L}earning\\
\textbf{NLP} & \textbf{N}atural \textbf{L}anguage \textbf{P}rocessing\\
\textbf{RC} & \textbf{R}ubiks' \textbf{C}ube\\
\textbf{RL} & \textbf{R}einforcment \textbf{L}earning\\
\textbf{RHUL} & \textbf{R}oyal \textbf{H}olloway, \textbf{U}niversity of \textbf{L}ondon\\
\textbf{SP} & \textbf{S}liding \textbf{P}uzzle\\

>>>>

\newcommand{\red}{\color{red}}
\newcommand{\black}{\color{black}}
\newcommand{\blue}{\color{blue}}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\afblue}{\color{airforceblue}}

@@

\usepackage{pythonhighlight}

@@

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
\textbf{Motivation}
\\
Reinforcement Learning (\textbf{RL}), exposed with brilliant clarity in the Sutton book (\cite{Sutton1998}), has until recently known less success than we might have hoped for. Its framework is very appealing and intuitive. In particular, the mathematical beauty of Value iteration and Q iteration (\cite{WatkinsThesis}) for discrete state and action spaces, blindly iterating from \textit{any} initial value, is quite profound. Sadly, it had until recently proven hard to achieve practical success with these methods.
\\
Inspired however by the seminal success of Deep Mind's team in using Deep Reinforcement Learning (\textbf{DRL}) to play Atari games (\cite{Mnih2013})  and to master the game of Go (\cite{AlphaGo}), researchers have in recent years made a lot of progress towards designing algorithms capable of learning and solving, \textit{without human knowledge}, the Rubiks Cube (\textbf{RC}) - as well as similar single player puzzles - by using Deep Q-Learning (\textbf{DQL})  (\cite{DBLP:journals/corr/abs-1805-07470}) or search and (\textbf{DRL}) value iteration (\cite{https://doi.org/10.48550/arxiv.1805.07470}).
\\
In this project, I will attempt to implement a variety of solvers combining $A^{*}$ search and heuristics, some of which will be handcrafted, others which I will train on randomly generated sequences of puzzles using (\textbf{DL}) or (\textbf{DRL}), to solve the 15-puzzle (and variations of different dimensions), as well as the Rubik's cube.
\\
\\
\textbf{Organisation of this thesis}
\\
In the first chapter, I will quickly describe what I hope to get out of this project, both in terms of personal learning, as well as in terms of tangible results (solving some puzzles!). In chapter 2, I will do a quick recap of the different methods that I will use in the project. Chapter 3 will be dedicated to discussing the mathematics of the sliding puzzle (\textbf{SP}) and the (\textbf{RC}). I might throw a few random (but hopefully interesting) observations in there and give some references for the keen reader. I will then give an overview in chapter 4 of the code base I have developed - and put in the open on my github page (\cite{FB}) - to complete this project before detailing a few examples in chapter 5. Finally, in chapters 6 and 7, I will present all my various results on respectively the sliding puzzle and the Rubiks' cube.

@@

\textbf{AIPnT} & \textbf{A}rtificial \textbf{I}ntelligence \textbf{P}rinciples and \textbf{T}echniques\\
\textbf{BFS} & \textbf{B}readth \textbf{F}irst \textbf{S}earch\\
\textbf{CS} & \textbf{C}omputer \textbf{S}cience\\
\textbf{CV} & \textbf{C}omputer \textbf{V}ision\\
\textbf{DFS} & \textbf{D}epth \textbf{F}irst \textbf{S}earch\\
\textbf{DL} & \textbf{D}eep \textbf{L}earning\\
\textbf{DQL} & \textbf{D}eep \textbf{Q}-\textbf{L}earning\\
\textbf{DRL} & \textbf{D}eep \textbf{R}einforcment \textbf{L}earning\\
\textbf{ML} & \textbf{M}achine \textbf{L}earning\\
\textbf{NLP} & \textbf{N}atural \textbf{L}anguage \textbf{P}rocessing\\
\textbf{RC} & \textbf{R}ubiks' \textbf{C}ube\\
\textbf{RL} & \textbf{R}einforcement \textbf{L}earning\\
\textbf{RHUL} & \textbf{R}oyal \textbf{H}olloway, \textbf{U}niversity of \textbf{L}ondon\\
\textbf{SP} & \textbf{S}liding \textbf{P}uzzle\\
